A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-25 paper/main.tex
revision of t-contrasts

\todo[inline]{die motion parameters werden nicht konvolviert, oder? MIH: Dunno.}

% t-contrasts
The following three t-contrasts were defined:
% 1b) no-speech > words;
% 2b) coordinate conjunctions > proper nouns;
% 3b) coordinate conjunctions > nouns.
1) words (all 21 \texttt{tag}-related regressors; N=15985) > no-speech (\texttt{no-sp}; N=\rNospAll),
2) proper nouns (\texttt{ne}; N=\rNeAll) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
3) nouns (\texttt{nn}; N=\rNeAll) > coordinate conjunctions.
\todo[inline]{I think having the N here is confusion. It is a contrast between regressors models. The number of events only indirectly accounts for the variance (which is interesting here). I would strip this info to reduce confusion}
% implementation detail. Any analysis should preserve the orientiation.
%The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].

% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied. In this way, long-time-scale components in the model will be dealt with correctly. This is set with the Apply temporal filtering option.”
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figures/regressor-corr}
  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation.
Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.}
\label{fig:reg-corr}
\end{figure*}

>>>>

% t-contrasts
The following three t-contrasts were defined:
1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions.
% 3b) coordinate conjunctions > nouns

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
    correlation coefficients of the 26 regressors used in the analysis to
    validate the annotation.
    Regressors were convolved with FSL's
    ``Double-Gamma HRF'' as a model of the hemodynamic response function and
    concatenated across runs before performing the correlation.}
\label{fig:reg-corr} \end{figure*}
